---
title: "Dicentrics dose estimation report"
author: "`r paste0('Biodose Tools', ' v', utils::packageVersion(pkg = 'biodosetools'))`"
date: "`r format(Sys.time(), '%d %B, %Y %H:%M:%S')`"
output: 
  pdf_document:
    number_sections: true
    extra_dependencies: ["graphicx", "newpxtext", "newpxmath"]
header-includes:
  - \usepackage{titling}
  - \pretitle{
    \vspace{-50pt}
    \includegraphics[width=2.0625in,height=0.5in]{`r system.file("/app/reports/logo.pdf", package = "biodosetools")`}\LARGE\\
    \begin{center}}
  - \posttitle{\end{center}}

params:
  est_results_list: NA
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(knitr)
```

```{r load-data, echo=FALSE}
assessment <- params$est_results_list[["assessment"]]

est_doses_whole <- params$est_results_list[["est_doses_whole"]]

est_doses_partial <- params$est_results_list[["est_doses_partial"]]
est_frac_partial <- params$est_results_list[["est_frac_partial"]]

est_mixing_prop_hetero <- params$est_results_list[["est_mixing_prop_hetero"]]
est_yields_hetero <- params$est_results_list[["est_yields_hetero"]]
est_doses_hetero <- params$est_results_list[["est_doses_hetero"]]
est_frac_hetero <- params$est_results_list[["est_frac_hetero"]]

AIC_whole <- params$est_results_list[["AIC_whole"]]
AIC_partial <- params$est_results_list[["AIC_partial"]]
AIC_hetero <- params$est_results_list[["AIC_hetero"]]

fit_coeffs <- params$est_results_list[["fit_coeffs"]]
fit_formula_tex <- params$est_results_list[["fit_formula_tex"]]
protraction <- params$est_results_list[["protraction"]]

case_data <- params$est_results_list[["case_data"]]
case_description <- params$est_results_list[["case_description"]]
results_comments <- params$est_results_list[["results_comments"]]
gg_curve <- params$est_results_list[["gg_curve"]]
```


# Curve used

## Fit formula

```{r echo=FALSE}
withMathJax(paste0("$$", fit_formula_tex, if (protraction[1]) "G(x)", "$$"))
```

`r if (protraction[1] ) paste("where")` 
`r if (protraction[1]) withMathJax("\\( G(x) \\)")` 
`r if (protraction[1]) paste("is a time-dependent correction that takes into account protracted and fractionated exposures:")`

```{r echo=FALSE}
if (protraction[1]) {
  withMathJax(paste0("$$", "G(x) = \\frac{2}{x^{2}} \\left(x - 1 - e^{-x} \\right), \\quad x = \\frac{t}{t_{0}}", "$$"))
}
```

`r if (protraction[1]) paste("The protraction times used for the dose estimation were")` 
`r if (protraction[1]) withMathJax(paste0("\\(", "t =", protraction[2]), "\\, \\textrm{h}", "\\)")` 
`r if (protraction[1]) paste("and")` 
`r if (protraction[1]) withMathJax(paste0("\\(", "t_{0} =", protraction[3]), "\\, \\textrm{h}", "\\)")` 
`r if (protraction[1]) paste(".")` 


## Coefficients

```{r echo=FALSE}
fit_coeffs %>%
  formatC(format = "e", digits = 3) %>%
  biodosetools:::fix_coeff_names(type = "rows", output = "kable") %>% 
  kable(booktabs = T, align = "c")
```


# Case data analyzed

\begin{centering}

```{r echo=FALSE}
case_data %>%
  as.matrix() %>% 
  formatC(format = "f", digits = 3) %>%
  as.data.frame() %>% 
  dplyr::mutate(
    dplyr::across(
      .cols = c("N", "X", dplyr::starts_with("C")),
      .fns = as.integer
    )    
  ) %>% 
  biodosetools:::fix_count_data_names(type = "case", output = "kable") %>% 
  kable(booktabs = T, align = "c", format = "latex", escape = FALSE)
  # TODO: Highlight u > 1.96 without kableExtra dependency
```

\end{centering}

## Case description

`r case_description`


# Dose estimation results

`r if (TRUE) {"## Whole-body exposure results"}`

`r if (TRUE) {"### Whole-body exposure estimation"}`

```{r echo=FALSE}
if (TRUE) {
  est_doses_whole %>%
    dplyr::select(yield) %>%
    t() %>%
    formatC(format = "f", digits = 3) %>%
    as.data.frame() %>%
    # Convert to hot and format table
    kable(booktabs = T, align = "c")
}
```

```{r echo=FALSE}
if (TRUE) {
  est_doses_whole %>%
    dplyr::select(`dose (Gy)` = dose) %>%
    t() %>%
    formatC(format = "f", digits = 3) %>%
    as.data.frame() %>%
    # Convert to hot and format table
    kable(booktabs = T, align = "c")
}
```

`r if (assessment == "partial-body") {"## Partial-body exposure results"}`

`r if (assessment == "partial-body") {"### Partial-body exposure estimation"}`

```{r echo=FALSE}
if (assessment == "partial-body") {
  est_doses_partial %>%
    dplyr::select(yield) %>%
    t() %>%
    formatC(format = "f", digits = 3) %>%
    as.data.frame() %>%
    # Fix possible NA values
    dplyr::mutate_if(is.logical, as.double) %>%
    `colnames<-`(c("lower", "estimate", "upper")) %>%
    `row.names<-`("yield") %>%
    # Convert to hot and format table
    kable(booktabs = T, align = "c")
}
```

```{r echo=FALSE}
if (assessment == "partial-body") {
  est_doses_partial %>%
    dplyr::select(dose) %>%
    t() %>%
    formatC(format = "f", digits = 3) %>%
    as.data.frame() %>%
    # Fix possible NA values
    dplyr::mutate_if(is.logical, as.double) %>%
    `colnames<-`(c("lower", "estimate", "upper")) %>%
    `row.names<-`("dose (Gy)") %>%
    # Convert to hot and format table
    kable(booktabs = T, align = "c")
}
```

`r if (assessment == "partial-body") {"### Initial fraction of irradiated cells"}`

```{r echo=FALSE}
if (assessment == "partial-body") {
  est_frac_partial %>%
    t() %>%
    formatC(format = "f", digits = 3) %>%
    as.data.frame() %>%
    # Fix possible NA values
    dplyr::mutate_if(is.logical, as.double) %>%
    `colnames<-`(c("lower", "estimate", "upper")) %>%
    `row.names<-`("fraction") %>%
    # Convert to hot and format table
    kable(booktabs = T, align = "c")
}
```

`r if (assessment == "hetero") {"## Heterogeneous exposure results"}`

`r if (assessment == "hetero") {"### Observed fraction of irradiated cells and its yield"}`

```{r echo=FALSE}
if (assessment == "hetero") {
  est_mixing_prop_hetero %>%
    as.matrix() %>% 
    formatC(format = "f", digits = 3) %>%
    as.data.frame() %>% 
    # Fix possible NA values
    dplyr::mutate_if(is.logical, as.double) %>%
    `colnames<-`(c("yield", "yield.err", "frac", "frac.err")) %>%
    `row.names<-`(c("dose1", "dose2")) %>%
    # Convert to hot and format table
    kable(booktabs = T, align = "c")
}
```

`r if (assessment == "hetero") {"### Heterogeneous exposure estimation"}`

```{r echo=FALSE}
if (assessment == "hetero") {
  est_yields_hetero %>%
    t() %>%
    formatC(format = "f", digits = 3) %>%
    as.data.frame() %>%
    # Fix possible NA values
    dplyr::mutate_if(is.logical, as.double) %>%
    `colnames<-`(c("lower", "estimate", "upper")) %>%
    `row.names<-`(c("yield1", "yield2")) %>%
    # Convert to hot and format table
    kable(booktabs = T, align = "c")
}
```

```{r echo=FALSE}
if (assessment == "hetero") {
  est_doses_hetero %>%
    t() %>%
    formatC(format = "f", digits = 3) %>%
    as.data.frame() %>%
    # Fix possible NA values
    dplyr::mutate_if(is.logical, as.double) %>%
    `colnames<-`(c("lower", "estimate", "upper")) %>%
    `row.names<-`(c("dose1 (Gy)", "dose2 (Gy)")) %>%
    # Convert to hot and format table
    kable(booktabs = T, align = "c")
}
```

`r if (assessment == "hetero") {"### Initial fraction of irradiated cells"}`

```{r echo=FALSE}
if (assessment == "hetero") {
  est_frac_hetero %>%
    # Fix possible NA values
    as.matrix() %>% 
    formatC(format = "f", digits = 3) %>%
    as.data.frame() %>% 
    dplyr::mutate_if(is.logical, as.double) %>%
    `colnames<-`(c("estimate", "std.err")) %>%
    `row.names<-`(c("dose1", "dose2")) %>%
    # Convert to hot and format table
    kable(booktabs = T, align = "c")
}
```

## Curve plot

```{r echo=FALSE, fig.width=6, fig.height=3}
gg_curve
```

## Comments

`r results_comments`
