---
title: "Dose estimation report"
author: "`r paste0('Biodose Tools', ' v', utils::packageVersion(pkg = 'biodosetools'))`"
date: "`r format(Sys.time(), '%d %B, %Y %H:%M:%S')`"
output: 
  html_document:
    css: !expr system.file("/app/reports/cosmo.css", package = "biodosetools")
    includes:
      before_body: !expr system.file("/app/reports/header.html", package = "biodosetools")
      after_body: !expr system.file("/app/reports/footer.html", package = "biodosetools")

params:
  est_results_list: NA
---

```{r include=FALSE}
library(dplyr)
library(ggplot2)
library(rhandsontable)
xfun::pkg_load2(c("base64enc", "htmltools", "mime"))
```

```{r include=FALSE}
embed_var <- function(x, ...) {
  # f = tempfile(fileext = '.rds')
  f <- paste("fitting-data-", Sys.Date(), ".rds", sep = "")
  saveRDS(x, f)
  xfun::embed_file(f, ...)
}
```

```{r load-data, echo=FALSE}
assessment <- params$est_results_list[["assessment"]]

est_doses_whole <- params$est_results_list[["est_doses_whole"]]

est_doses_partial <- params$est_results_list[["est_doses_partial"]]
est_frac_partial <- params$est_results_list[["est_frac_partial"]]

est_mixing_prop_hetero <- params$est_results_list[["est_mixing_prop_hetero"]]
est_yields_hetero <- params$est_results_list[["est_yields_hetero"]]
est_doses_hetero <- params$est_results_list[["est_doses_hetero"]]
est_frac_hetero <- params$est_results_list[["est_frac_hetero"]]

AIC_whole <- params$est_results_list[["AIC_whole"]]
AIC_partial <- params$est_results_list[["AIC_partial"]]
AIC_hetero <- params$est_results_list[["AIC_hetero"]]

fit_coeffs <- params$est_results_list[["fit_coeffs"]]
fit_formula_tex <- params$est_results_list[["fit_formula_tex"]]
protraction <- params$est_results_list[["protraction"]]

case_data <- params$est_results_list[["case_data"]]
case_description <- params$est_results_list[["case_description"]]
results_comments <- params$est_results_list[["results_comments"]]
gg_curve <- params$est_results_list[["gg_curve"]]

genome_fraction <- params$est_results_list[["genome_fraction"]]
chromosome_table <- params$est_results_list[["chromosome_table"]]
trans_sex <- params$est_results_list[["trans_sex"]]
confounders <- params$est_results_list[["confounders"]]
```


## Curve used

### Fit formula

```{r echo=FALSE}
withMathJax(paste0("$$", fit_formula_tex, if (protraction[1]) "G(x)", "$$"))
```

`r if (protraction[1] ) paste("where")`
`r if (protraction[1]) withMathJax("\\( G(x) \\)")`
`r if (protraction[1]) paste("is a time-dependent correction that takes into account protracted and fractionated exposures:")`

```{r echo=FALSE}
if (protraction[1]) {
  withMathJax(paste0("$$", "G(x) = \\frac{2}{x^{2}} \\left(x - 1 - e^{-x} \\right), \\quad x = \\frac{t}{t_{0}}", "$$"))
}
```

`r if (protraction[1]) paste("The protraction times used for the dose estimation were")`
`r if (protraction[1]) withMathJax(paste0("\\(", "t =", protraction[2]), "\\, \\textrm{h}", "\\)")`
`r if (protraction[1]) paste("and")`
`r if (protraction[1]) withMathJax(paste0("\\(", "t_{0} =", protraction[3]), "\\, \\textrm{h}", "\\)")`
`r if (protraction[1]) paste(".")`

### Full genome coefficients

```{r echo=FALSE}
num_cols <- as.numeric(ncol(fit_coeffs))

fit_coeffs %>%
  formatC(format = "e", digits = 3) %>%
  # as.data.frame() %>%
  # dplyr::select(-statistic) %>%
  # as.matrix() %>%
  # Convert to hot and format table
  rhandsontable(
    width = (50 + num_cols * 100), 
    height = "100%",
    rowHeaders = c("C", "\u03B1", "\u03B2")
  ) %>%
  hot_cols(colWidths = 100) %>%
  hot_cols(halign = "htRight")
```


## Case chromosome data

The analyzed blood sample comes from a `r trans_sex` individual.

```{r echo=FALSE}
num_cols <- as.numeric(ncol(chromosome_table))

hot <- chromosome_table %>%
  rhandsontable(
    width = (80 + num_cols * 85), 
    height = "100%"
  ) %>%
  hot_col(1, colWidths = 115, readOnly = TRUE) %>%
  hot_cols(halign = "htCenter")

if (num_cols > 1) {
  hot <- hot %>%
    hot_col(2:num_cols, colWidths = 85)
}

hot
```

### Genomic conversion factor

`r paste0("The genomic conversion factor to full genome is ", genome_fraction %>% round(3) %>%  as.character(), ".")`


## Case data analyzed

```{r echo=FALSE}
# Read number of columns
num_cols <- as.numeric(ncol(case_data))

# Convert to hot and format table
case_data %>%
  rhandsontable(
    width = (50 + num_cols * 50), 
    height = "100%"
  ) %>%
  hot_cols(colWidths = 50) %>%
  # hot_table(highlightCol = TRUE, highlightRow = TRUE)
  hot_col(c(1, 2, seq(num_cols - 6, num_cols, 1)), readOnly = TRUE) %>%
  hot_col(num_cols - 3, renderer = "
     function (instance, td, row, col, prop, value, cellProperties) {
       Handsontable.renderers.NumericRenderer.apply(this, arguments);
       if (value > 1.96) {
        td.style.background = 'pink';
       }
     }")
```

### Confounders

`r if (is.null(confounders)) paste("No confounders were selected.")`
`r if (!is.null(confounders) & length(confounders) == 1) paste0("To account for confounders, the following translocation frequency per cell was manually input: ", confounders, ".")`

`r if (!is.null(confounders) & length(confounders) > 1) paste("The following confounders were selected:")`
```{r echo=FALSE}
if (!is.null(confounders) & length(confounders) > 1) {
  confounders %>%
    as.matrix() %>%
    t() %>%
    as.data.frame() %>%
    mutate(
      sex_bool = with(., case_when(
        (sex_bool == TRUE) ~ "Used",
        (sex_bool == FALSE) ~ "Not used"
      )),
      smoker_bool = with(., case_when(
        (smoker_bool == TRUE) ~ "Yes",
        (smoker_bool == FALSE) ~ "No"
      )),
      ethnicity_value = with(., case_when(
        (ethnicity_value == "white") ~ "White",
        (ethnicity_value == "asian") ~ "Asian",
        (ethnicity_value == "black") ~ "Black",
        (ethnicity_value == "other") ~ "Others",
        TRUE ~ "Not specified"
      )),
      region_value = with(., case_when(
        (region_value == "n-america") ~ "North America",
        (region_value == "w-europe") ~ "Western Europe",
        (region_value == "c-europe") ~ "Central Europe",
        (region_value == "e-europe") ~ "Eastern Europe",
        (region_value == "asia") ~ "Asia",
        TRUE ~ "Not specified"
      ))
    ) %>%
    `colnames<-`(c("Age", "Sex", "Smoker", "Ethnicity", "Lab region")) %>%
    rhandsontable(
      width = 625, height = "100%", 
      rowHeaders = NULL
    ) %>%
    hot_cols(colWidths = 125, halign = "htCenter")
}
```

### Case description

`r case_description`


## Dose estimation results

`r if (TRUE) {"### Whole-body exposure results"}`

`r if (TRUE) {"#### Whole-body exposure estimation"}`

```{r echo=FALSE}
if (TRUE) {
  est_doses_whole %>%
    dplyr::select(yield) %>%
    t() %>%
    as.data.frame() %>%
    # Convert to hot and format table
    rhandsontable(
      width = 320, height = "100%", 
      rowHeaderWidth = 80
    ) %>%
    hot_cols(colWidths = 80) %>%
    hot_cols(format = "0.000")
}
```

```{r echo=FALSE}
if (TRUE) {
  est_doses_whole %>%
    dplyr::select(dose) %>%
    t() %>%
    as.data.frame() %>%
    # Convert to hot and format table
    rhandsontable(
      width = 320, 
      height = "100%", 
      rowHeaders = "dose (Gy)", 
      rowHeaderWidth = 80
    ) %>%
    hot_cols(colWidths = 80) %>%
    hot_cols(format = "0.000")
}
```

<!-- `r if (TRUE) {"#### Relative quality of the estimation"}` -->
<!-- ```{r echo=FALSE} -->
<!-- if (TRUE) { -->
<!--   AIC_whole %>% -->
<!--     matrix() %>% -->
<!--     `colnames<-`(c("AIC")) %>% -->
<!--     rhandsontable(width = 80, height = "100%") %>% -->
<!--     hot_cols(colWidths = 80) %>% -->
<!--     hot_cols(format = "0.000") -->
<!-- } -->
<!-- ``` -->

`r if (assessment == "partial-body") {"### Partial-body exposure results"}`

`r if (assessment == "partial-body") {"#### Partial-body exposure estimation"}`

```{r echo=FALSE}
if (assessment == "partial-body") {
  est_doses_partial %>%
    dplyr::select(yield) %>%
    t() %>%
    as.data.frame() %>%
    # Fix possible NA values
    dplyr::mutate_if(is.logical, as.double) %>%
    `colnames<-`(c("lower", "estimate", "upper")) %>%
    `row.names<-`("yield") %>%
    # Convert to hot and format table
    rhandsontable(
      width = 320, 
      height = "100%", 
      rowHeaderWidth = 80
    ) %>%
    hot_cols(colWidths = 80) %>%
    hot_cols(format = "0.000")
}
```

```{r echo=FALSE}
if (assessment == "partial-body") {
  est_doses_partial %>%
    dplyr::select(dose) %>%
    t() %>%
    as.data.frame() %>%
    # Fix possible NA values
    dplyr::mutate_if(is.logical, as.double) %>%
    `colnames<-`(c("lower", "estimate", "upper")) %>%
    `row.names<-`("dose (Gy)") %>%
    # Convert to hot and format table
    rhandsontable(
      width = 320, 
      height = "100%", 
      rowHeaderWidth = 80
    ) %>%
    hot_cols(colWidths = 80) %>%
    hot_cols(format = "0.000")
}
```

`r if (assessment == "partial-body") {"#### Initial fraction of irradiated cells"}`

```{r echo=FALSE}
if (assessment == "partial-body") {
  est_frac_partial %>%
    t() %>%
    as.data.frame() %>%
    # Fix possible NA values
    dplyr::mutate_if(is.logical, as.double) %>%
    `colnames<-`(c("lower", "estimate", "upper")) %>%
    `row.names<-`("fraction") %>%
    # Convert to hot and format table
    rhandsontable(
      width = 320, 
      height = "100%", 
      rowHeaderWidth = 80
    ) %>%
    hot_cols(colWidths = 80) %>%
    hot_cols(format = "0.000")
}
```

<!-- `r if (assessment == "partial-body") {"#### Relative quality of the estimation"}` -->
<!-- ```{r echo=FALSE} -->
<!-- if (assessment == "partial-body") { -->
<!--   AIC_partial %>% -->
<!--     matrix() %>% -->
<!--     `colnames<-`(c("AIC")) %>% -->
<!--     rhandsontable(width = 80, height = "100%") %>% -->
<!--     hot_cols(colWidths = 80) %>% -->
<!--     hot_cols(format = "0.000") -->
<!-- } -->
<!-- ``` -->

### Curve plot

```{r echo=FALSE}
gg_curve
```

### Comments

`r results_comments`
