---
title: "Translocation FISH curve fitting report"
author: "`r paste0('Biodose Tools', ' v', utils::packageVersion(pkg = 'biodosetools'))`"
date: "`r format(Sys.time(), '%d %B, %Y %H:%M:%S')`"
output: 
  pdf_document:
    number_sections: true
    extra_dependencies: ["graphicx", "newpxtext", "newpxmath"]
header-includes:
  - \usepackage{titling}
  - \pretitle{
    \vspace{-50pt}
    \includegraphics[width=2.0625in,height=0.5in]{`r system.file("/app/reports/logo.pdf", package = "biodosetools")`}\LARGE\\
    \begin{center}}
  - \posttitle{\end{center}}

params:
  fit_results_list: NA
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(knitr)
```

```{r load-data, echo=FALSE}
count_data <- params$fit_results_list[["fit_raw_data"]]
fit_model_statistics <- params$fit_results_list[["fit_model_statistics"]]
fit_model_summary <- params$fit_results_list[["fit_model_summary"]]
fit_coeffs <- params$fit_results_list[["fit_coeffs"]]
fit_var_cov_mat <- params$fit_results_list[["fit_var_cov_mat"]]
fit_cor_mat <- params$fit_results_list[["fit_cor_mat"]]
fit_formula_tex <- params$fit_results_list[["fit_formula_tex"]]
gg_curve <- params$fit_results_list[["gg_curve"]]
# detection_lims <- params$fit_results_list[["detection_lims"]]

genome_fraction <- params$fit_results_list[["genome_fraction"]]
chromosome_table <- params$fit_results_list[["chromosome_table"]]
trans_sex <- params$fit_results_list[["trans_sex"]]
frequency_select <- params$fit_results_list[["frequency_select"]]
```


# Chromosome data

The analyzed blood sample comes from a `r trans_sex` individual.

```{r echo=FALSE}
num_cols <- as.numeric(ncol(chromosome_table))

chromosome_table %>%
  dplyr::mutate(
    dplyr::across(
      .cols = dplyr::everything(),
      .fns = function(x) {
        x <- ifelse(is.na(x) | x == "FALSE", "", x)
        x <- ifelse(x == "TRUE", "$\\checkmark$", x)
        return(x)
      }
    )
  ) %>% 
  kable(booktabs = T, align = "c")
```

`r if (num_cols == 1) paste("where each chromosome was stained using M-FISH.")`


# Count data used

```{r echo=FALSE}
col_headers <- colnames(count_data)
col_headers[1] <- paste(col_headers[1], "(Gy)")
colnames(count_data) <- col_headers

count_data %>% 
  kable(booktabs = T, align = "c")
  # TODO: Highlight u > 1.96 without kableExtra dependency
```


# Results

## Fit formula

```{r echo=FALSE}
shiny::withMathJax(paste0("$$", fit_formula_tex, "$$"))
```

## Model

`r gsub("≤", "$\\\\leq$", fit_model_summary)`

## Translocation frequency

`r paste("The fitting was performed using the ")`
`r if (frequency_select == "full_gen_freq") paste("full genome translocation frequency.") else if (frequency_select == "measured_freq") paste("translocation frequency measured by FISH.")`

## Genomic conversion factor

`r paste0("The genomic conversion factor to full genome is ", genome_fraction %>% round(3) %>%  as.character(), ".")`

## Coefficients

```{r echo=FALSE}
fit_coeffs %>%
  formatC(format = "e", digits = 3) %>%
  biodosetools:::fix_coeff_names(type = "rows", output = "kable") %>% 
  kable(booktabs = T, align = "c")
```

## Model-level statistics

```{r echo=FALSE}
fit_model_statistics %>%
  kable(booktabs = T, align = "c")
```

## Correlation matrix

```{r echo=FALSE}
fit_cor_mat %>%
  biodosetools:::fix_coeff_names(type = "rows", output = "kable") %>% 
  biodosetools:::fix_coeff_names(type = "cols", output = "kable") %>% 
  formatC(format = "f", digits = 3) %>%
  kable(booktabs = T, align = "c")
```

## Variance-covariance matrix

```{r echo=FALSE}
fit_var_cov_mat %>%
  biodosetools:::fix_coeff_names(type = "rows", output = "kable") %>% 
  biodosetools:::fix_coeff_names(type = "cols", output = "kable") %>% 
  formatC(format = "e", digits = 3) %>%
  kable(booktabs = T, align = "c")
```

## Curve plot

```{r echo=FALSE, fig.width=6, fig.height=3}
gg_curve
```

## Download fit results

The PDF format does not support embedded files. You can only save the results in RDS format from Biodose Tools or from the HTML report.
