---
title: "Dose estimation report"
author: "`r paste('Biodose Tools', '-', app_version)`"
date: "`r format(Sys.time(), '%d %B, %Y %H:%M:%S')`"
output: word_document
params:
  est_results_list: NA
---

```{r include=FALSE}
library(xfun)
xfun::pkg_load2(c('base64enc', 'htmltools', 'mime'))
```

```{r include=FALSE}
embed_var <- function(x, ...) {
  # f = tempfile(fileext = '.rds')
  f = paste("fitting-data-", Sys.Date(), ".rds", sep = "")
  saveRDS(x, f)
  xfun::embed_file(f, ...)
}
```

```{r load-data, echo=FALSE}
assessment <- params$est_results_list[["assessment"]]

est_doses_whole <- params$est_results_list[["est_doses_whole"]]

est_doses_partial <- params$est_results_list[["est_doses_partial"]]
est_frac_partial <- params$est_results_list[["est_frac_partial"]]

est_mixing_prop_hetero <- params$est_results_list[["est_mixing_prop_hetero"]]
est_yields_hetero <- params$est_results_list[["est_yields_hetero"]]
est_doses_hetero <- params$est_results_list[["est_doses_hetero"]]
est_frac_hetero <- params$est_results_list[["est_frac_hetero"]]

AIC_whole <- params$est_results_list[["AIC_whole"]]
AIC_partial <- params$est_results_list[["AIC_partial"]]
AIC_hetero <- params$est_results_list[["AIC_hetero"]]

fit_coeffs <- params$est_results_list[["fit_coeffs"]]
fit_formula_tex <- params$est_results_list[["fit_formula_tex"]]
protraction <- params$est_results_list[["protraction"]]

case_data <- params$est_results_list[["case_data"]]
case_description <- params$est_results_list[["case_description"]]
results_comments <- params$est_results_list[["results_comments"]]
gg_curve <- params$est_results_list[["gg_curve"]]

genome_fraction <- params$est_results_list[["genome_fraction"]]
chromosome_table <- params$est_results_list[["chromosome_table"]]
trans_sex <- params$est_results_list[["trans_sex"]]
confounders <- params$est_results_list[["confounders"]]
```


## Curve used

### Fit formula
```{r echo=FALSE}
withMathJax(paste0("$$", fit_formula_tex, if (protraction[1]) "G(x)", "$$"))
```

`r if (protraction[1] ) paste("where")` 
`r if (protraction[1]) withMathJax("\\( G(x) \\)")` 
`r if (protraction[1]) paste("is a time-dependent correction that takes into account protracted and fractionated exposures:")`
```{r echo=FALSE}
if (protraction[1]) {
  withMathJax(paste0("$$", "G(x) = \\frac{2}{x^{2}} \\left(x - 1 - e^{-x} \\right), \\quad x = \\frac{t}{t_{0}}", "$$"))
}
```
`r if (protraction[1]) paste("The protraction times used for the dose estimation were")` 
`r if (protraction[1]) withMathJax(paste0("\\(", "t =", protraction[2]), "\\, \\textrm{h}", "\\)")` 
`r if (protraction[1]) paste("and")` 
`r if (protraction[1]) withMathJax(paste0("\\(", "t_{0} =", protraction[3]), "\\, \\textrm{h}", "\\)")` 
`r if (protraction[1]) paste(".")` 


### Full genome coefficients
```{r echo=FALSE}
fit_coeffs %>%
  formatC(format = "e", digits = 3) %>%
  # as.data.frame() %>%
  # dplyr::select(-statistic) %>%
  # as.matrix() %>%
  pander::pander()
```

## Case chromosome data

The analyzed blood sample comes from a `r trans_sex` individual.

```{r echo=FALSE}
num_cols <- ncol(chromosome_table)

chromosome_table <- chromosome_table %>% 
  as.data.frame() 

if (num_cols > 1) {
  chromosome_table <- chromosome_table %>% 
    mutate_at(seq(2, num_cols , 1), function(x) {
      case_when(
        is.na(x) ~ "",
        (x == "FALSE") ~ "",
        (x == "TRUE") ~ "x",
      )
    })
}

chromosome_table%>% 
  pander::pander()
```

### Genomic conversion factor
`r paste0("The genomic conversion factor to full genome is ", genome_fraction %>% round(3) %>%  as.character(), ".")`

## Case data analyzed
```{r echo=FALSE}
case_data %>%
  pander::pander()
  # TODO: Add u-value highlighting
```

### Confounders

`r if (is.null(confounders)) paste("No confounders were selected.")`
`r if (!is.null(confounders) & length(confounders) == 1) paste0("To account for confounders, the following translocation frequency per cell was manually input: ", confounders, ".")`

`r if (!is.null(confounders) & length(confounders) > 1) paste("The following confounders were selected:")`
```{r echo=FALSE}
if (!is.null(confounders) & length(confounders) > 1) {
  confounders %>%
    as.matrix() %>%
    t() %>%
    as.data.frame() %>%
    mutate(
      sex_bool = with(., case_when(
        (sex_bool == TRUE)  ~ "Used", 
        (sex_bool == FALSE) ~ "Not used"
      )),
      smoker_bool = with(., case_when(
        (smoker_bool == TRUE)  ~ "Yes", 
        (smoker_bool == FALSE) ~ "No"
      )),
      ethnicity_value = with(., case_when(
        (ethnicity_value == "white") ~ "White", 
        (ethnicity_value == "asian") ~ "Asian", 
        (ethnicity_value == "black") ~ "Black", 
        (ethnicity_value == "other") ~ "Others",
        TRUE ~ "Not specified"
      )),
      region_value = with(., case_when(
        (region_value == "n-america") ~ "North America",
        (region_value == "w-europe")  ~ "Western Europe",
        (region_value == "c-europe")  ~ "Central Europe",
        (region_value == "e-europe")  ~ "Eastern Europe",
        (region_value == "asia")      ~ "Asia",
        TRUE ~ "Not specified"
      ))
    ) %>%
    `colnames<-`(c("Age", "Sex", "Smoker", "Ethnicity", "Lab region")) %>%
    pander::pander()
}
```

### Case description
`r case_description`

## Dose estimation results

`r if (TRUE) {"### Whole-body exposure results"}`

`r if (TRUE) {"#### Whole-body exposure estimation"}`
```{r echo=FALSE}
if (TRUE) {
  est_doses_whole %>%
    dplyr::select(yield) %>%
    t() %>%
    formatC(format = "f", digits = 3) %>% 
    pander::pander()
} 
```

`r if (TRUE) {"####"}`

```{r echo=FALSE}
if (TRUE) {
  est_doses_whole %>%
    dplyr::select(dose) %>%
    t() %>%
    # as.data.frame() %>%
    formatC(format = "f", digits = 3) %>% 
    pander::pander()
} 
```

<!-- `r if (TRUE) {"#### Relative quality of the estimation"}` -->
<!-- ```{r echo=FALSE} -->
<!-- if (TRUE) { -->
<!--   AIC_whole %>% -->
<!--     matrix() %>% -->
<!--     `colnames<-`(c("AIC")) %>% -->
<!--     formatC(format = "f", digits = 3) %>%  -->
<!--     pander::pander() -->
<!-- }  -->
<!-- ``` -->

`r if (assessment == "partial-body") {"### Partial-body exposure results"}`

`r if (assessment == "partial-body") {"#### Partial-body exposure estimation"}`
```{r echo=FALSE}
if (assessment == "partial-body") {
  est_doses_partial %>%
    dplyr::select(yield) %>%
    t() %>%
    formatC(format = "f", digits = 3) %>% 
    as.data.frame() %>%
    # Fix possible NA values
    dplyr::mutate_if(is.logical, as.double) %>%
    `colnames<-`(c("lower", "estimate", "upper")) %>%
    `row.names<-`("yield") %>%
    pander::pander()
} 
```

`r if (assessment == "partial-body") {"####"}`
```{r echo=FALSE}
if (assessment == "partial-body") {
  est_doses_partial%>%
    dplyr::select(dose) %>%
    t() %>%
    formatC(format = "f", digits = 3) %>% 
    as.data.frame() %>%
    # Fix possible NA values
    dplyr::mutate_if(is.logical, as.double) %>%
    `colnames<-`(c("lower", "estimate", "upper")) %>%
    `row.names<-`("dose (Gy)") %>%
    pander::pander()
} 
```

`r if (assessment == "partial-body") {"#### Initial fraction of irradiated cells"}`
```{r echo=FALSE}
if (assessment == "partial-body") {
  est_frac_partial %>%
    t() %>%
    formatC(format = "f", digits = 3) %>% 
    as.data.frame() %>%
    # Fix possible NA values
    dplyr::mutate_if(is.logical, as.double) %>%
    `colnames<-`(c("lower", "estimate", "upper")) %>%
    `row.names<-`("fraction") %>%
    pander::pander()
} 
```

<!-- `r if (assessment == "partial-body") {"#### Relative quality of the estimation"}` -->
<!-- ```{r echo=FALSE} -->
<!-- if (assessment == "partial-body") { -->
<!--   AIC_partial %>% -->
<!--     matrix() %>% -->
<!--     `colnames<-`(c("AIC")) %>% -->
<!--     formatC(format = "f", digits = 3) %>%  -->
<!--     pander::pander() -->
<!-- }  -->
<!-- ``` -->

### Curve plot
```{r echo=FALSE}
gg_curve
```

### Comments
`r results_comments`
