---
title: "Dose estimation report"
author: "`r paste('Biodose Tools', '-', app_version)`"
date: "`r format(Sys.time(), '%d %B, %Y %H:%M:%S')`"
output: word_document
params:
  est_results_list: NA
---

```{r include=FALSE}
pander::panderOptions("table.style", "grid")
```

```{r load-data, echo=FALSE}
assessment <- params$est_results_list[["assessment"]]

est_doses_whole <- params$est_results_list[["est_doses_whole"]]

est_doses_partial <- params$est_results_list[["est_doses_partial"]]
est_frac_partial <- params$est_results_list[["est_frac_partial"]]

est_mixing_prop_hetero <- params$est_results_list[["est_mixing_prop_hetero"]]
est_yields_hetero <- params$est_results_list[["est_yields_hetero"]]
est_doses_hetero <- params$est_results_list[["est_doses_hetero"]]
est_frac_hetero <- params$est_results_list[["est_frac_hetero"]]

AIC_whole <- params$est_results_list[["AIC_whole"]]
AIC_partial <- params$est_results_list[["AIC_partial"]]
AIC_hetero <- params$est_results_list[["AIC_hetero"]]

fit_coeffs <- params$est_results_list[["fit_coeffs"]]
fit_formula_tex <- params$est_results_list[["fit_formula_tex"]]
protraction <- params$est_results_list[["protraction"]]

case_data <- params$est_results_list[["case_data"]]
case_description <- params$est_results_list[["case_description"]]
results_comments <- params$est_results_list[["results_comments"]]
gg_curve <- params$est_results_list[["gg_curve"]]
```

## Curve used

### Fit formula
```{r echo=FALSE}
withMathJax(paste0("$$", fit_formula_tex, if (protraction[1]) "G(x)", "$$"))
```

`r if (protraction[1] ) paste("where")` 
`r if (protraction[1]) withMathJax("\\( G(x) \\)")` 
`r if (protraction[1]) paste("is a time-dependent correction that takes into account protracted and fractionated exposures:")`
```{r echo=FALSE}
if (protraction[1]) {
  withMathJax(paste0("$$", "G(x) = \\frac{2}{x^{2}} \\left(x - 1 - e^{-x} \\right), \\quad x = \\frac{t}{t_{0}}", "$$"))
}
```
`r if (protraction[1]) paste("The protraction times used for the dose estimation were")` 
`r if (protraction[1]) withMathJax(paste0("\\(", "t =", protraction[2]), "\\, \\textrm{h}", "\\)")` 
`r if (protraction[1]) paste("and")` 
`r if (protraction[1]) withMathJax(paste0("\\(", "t_{0} =", protraction[3]), "\\, \\textrm{h}", "\\)")` 
`r if (protraction[1]) paste(".")` 


### Coefficients
```{r echo=FALSE}
fit_coeffs %>%
  formatC(format = "e", digits = 3) %>%
  # as.data.frame() %>%
  # dplyr::select(-statistic) %>%
  # as.matrix() %>%
  pander::pander()
  
```



## Case data analyzed
```{r echo=FALSE}
case_data %>%
  pander::pander()
  # TODO: Add u-value highlighting
```

### Case description
`r case_description`

## Dose estimation results

`r if (TRUE) {"### Whole-body exposure results"}`

`r if (TRUE) {"#### Whole-body exposure estimation"}`
```{r echo=FALSE}
if (TRUE) {
  est_doses_whole %>%
    dplyr::select(yield) %>%
    t() %>%
    formatC(format = "f", digits = 3) %>% 
    pander::pander()
} 
```

`r if (TRUE) {"####"}`

```{r echo=FALSE}
if (TRUE) {
  est_doses_whole %>%
    dplyr::select(dose) %>%
    t() %>%
    # as.data.frame() %>%
    formatC(format = "f", digits = 3) %>% 
    pander::pander()
} 
```

`r if (TRUE) {"#### Relative quality of the estimation"}`
```{r echo=FALSE}
if (TRUE) {
  AIC_whole %>%
    matrix() %>%
    `colnames<-`(c("AIC")) %>%
    formatC(format = "f", digits = 3) %>% 
    pander::pander()
} 
```

`r if (assessment == "partial-body") {"### Partial-body exposure results"}`

`r if (assessment == "partial-body") {"#### Partial-body exposure estimation"}`
```{r echo=FALSE}
if (assessment == "partial-body") {
  est_doses_partial %>%
    dplyr::select(yield) %>%
    t() %>%
    as.data.frame() %>%
    # Fix possible NA values
    dplyr::mutate_if(is.logical, as.double) %>%
    `colnames<-`(c("lower", "estimate", "upper")) %>%
    `row.names<-`("yield") %>%
    formatC(format = "f", digits = 3) %>% 
    pander::pander()
} 
```

`r if (assessment == "partial-body") {"####"}`
```{r echo=FALSE}
if (assessment == "partial-body") {
  est_doses_partial%>%
    dplyr::select(dose) %>%
    t() %>%
    as.data.frame() %>%
    # Fix possible NA values
    dplyr::mutate_if(is.logical, as.double) %>%
    `colnames<-`(c("lower", "estimate", "upper")) %>%
    `row.names<-`("dose (Gy)") %>%
    formatC(format = "f", digits = 3) %>% 
    pander::pander()
} 
```

`r if (assessment == "partial-body") {"#### Initial fraction of irradiated cells"}`
```{r echo=FALSE}
if (assessment == "partial-body") {
  est_frac_partial %>%
    t() %>%
    as.data.frame() %>%
    # Fix possible NA values
    dplyr::mutate_if(is.logical, as.double) %>%
    `colnames<-`(c("lower", "estimate", "upper")) %>%
    `row.names<-`("fraction") %>%
    formatC(format = "f", digits = 3) %>% 
    pander::pander()
} 
```

`r if (assessment == "partial-body") {"#### Relative quality of the estimation"}`
```{r echo=FALSE}
if (assessment == "partial-body") {
  AIC_partial %>%
    matrix() %>%
    `colnames<-`(c("AIC")) %>%
    formatC(format = "f", digits = 3) %>% 
    pander::pander()
} 
```

`r if (assessment == "hetero") {"### Heterogeneous exposure results"}`

`r if (assessment == "hetero") {"#### Observed fraction of irradiated cells and its yield"}`
```{r echo=FALSE}
if (assessment == "hetero") {
  est_mixing_prop_hetero %>%
    # Fix possible NA values
    dplyr::mutate_if(is.logical, as.double) %>%
    `colnames<-`(c("yield", "yield.err", "frac", "frac.err")) %>%
    `row.names<-`(c("dose1", "dose2")) %>%
    as.matrix() %>% 
    formatC(format = "f", digits = 3) %>%
    pander::pander()
}
```

`r if (assessment == "hetero") {"#### Heterogeneous exposure estimation"}`
```{r echo=FALSE}
if (assessment == "hetero") {
  est_yields_hetero %>%
    t() %>%
    formatC(format = "f", digits = 3) %>%
    as.data.frame() %>%
    # Fix possible NA values
    dplyr::mutate_if(is.logical, as.double) %>%
    `colnames<-`(c("lower", "estimate", "upper")) %>%
    `row.names<-`(c("yield1", "yield2")) %>%
    pander::pander()
}
```

`r if (assessment == "hetero") {"####"}`

```{r echo=FALSE}
if (assessment == "hetero") {
  est_doses_hetero %>%
    t() %>%
    formatC(format = "f", digits = 3) %>%
    as.data.frame() %>%
    # Fix possible NA values
    dplyr::mutate_if(is.logical, as.double) %>%
    `colnames<-`(c("lower", "estimate", "upper")) %>%
    `row.names<-`(c("dose1 (Gy)", "dose2 (Gy)")) %>%
    pander::pander()
}
```

`r if (assessment == "hetero") {"#### Initial fraction of irradiated cells"}`
```{r echo=FALSE}
if (assessment == "hetero") {
  est_frac_hetero %>%
    # Fix possible NA values
    dplyr::mutate_if(is.logical, as.double) %>%
    `colnames<-`(c("estimate", "std.err")) %>%
    `row.names<-`(c("dose1", "dose2")) %>%
    as.matrix() %>% 
    formatC(format = "f", digits = 3) %>%
    pander::pander()
}
```

`r if (assessment == "hetero") {"#### Relative quality of the estimation"}`
```{r echo=FALSE}
if (assessment == "hetero") {
  AIC_hetero %>%
    matrix() %>%
    `colnames<-`(c("AIC")) %>%
    formatC(format = "f", digits = 3) %>% 
    pander::pander()
} 
```

### Curve plot
```{r echo=FALSE}
gg_curve
```

### Comments
`r results_comments`
